Active learning for efficient systematic reviews

### 2020-07-20 Ferdinands,-G---MSBBSS.Rmd
corrctions July 20 2020

---
title: Active learning for efficient systematic reviews
subtitle: Evaluating models across research areas 
author: "Gerbrich Ferdinands"
# keywords:
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage[left]{lineno}
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::pdf_document2:
    extra_dependencies: subfig, algorithm2e, float
    number_sections: no
    toc: no
  word_document: default
bibliography: asreview.bib
link-citations: yes
csl: elsevier-vancouver.csl
---

@@

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.ncol = 2, out.width = "50%", fig.align = "center", fig.pos = "H") 
options(tinytex.verbose = TRUE)

@@

```{r, eval = TRUE, fig-sub-alldata, fig.cap = "Recall curves of all seven models for all  indicating how fast the model finds relevant publications during the process of screening publications.  on (a) the PTSD, (b) Software, (c) Ace, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","Ace","Virus","Wilson")}
d <- c("ptsd", "software", "ace", "virus", "wilson")
files <- c("../../results/one_seed/plots/ptsd/inclusion_all_ptsd.pdf" ,paste0("../../results/one_seed/plots/", d[2:5], "/nolegend_inclusion_all_", d[2:5], ".pdf"))
include_graphics(files)
```

>>>>

---
title: Active learning for efficient systematic reviews
subtitle: Evaluating models across research areas 
author: "G. Ferdinands, R.D. Schram, J. de Bruin, A. Bagheri, D. Oberski, L. Tummers, R. van de Schoot"
# keywords:
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage[left]{lineno}
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::pdf_document2:
    extra_dependencies: subfig, algorithm2e, float
    number_sections: no
    toc: no
  word_document: default
bibliography: asreview.bib
link-citations: yes
csl: elsevier-vancouver.csl
---

@@

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.ncol = 2, out.width = "50%", fig.align = "center",fig.path = "figures/", dev = "png", fig.pos = "H") 
options(tinytex.verbose = TRUE)

@@

```{r, eval = TRUE, fig-sub-alldata, fig.cap = "Recall curves of all seven models for all  indicating how fast the model finds relevant publications during the process of screening publications.  on (a) the PTSD, (b) Software, (c) Ace, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","Ace","Virus","Wilson")}
d <- c("ptsd", "software", "ace", "virus", "wilson")
files <- c("../../results/one_seed/plots/ptsd/inclusion_all_ptsd.pdf" ,paste0("../../results/one_seed/plots/", d[2:5], "/nolegend_inclusion_all_", d[2:5], ".pdf"))

include_graphics(files)
```
